Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method

### 2019-11-11 rainbowCAM.tex
Added a figure showing the effective potential (thanks Tom!)

We shall consider a scalar wave $\Phi(x)$ on the compact body spacetime governed by the Klein-Gordon equation
\begin{equation}
\Box \Phi \equiv \frac{1}{\sqrt{-g}} \partial_{\mu} \left( \sqrt{-g} g^{\mu \nu} \partial_{\nu} \Phi \right) = 0
\end{equation}
where $g^{\mu \nu}$ is the inverse metric 
$
g = - f(r) h^{-1}(r) r^4 \sin^2 \theta
$
and is the metric determinant. Performing a standard separation of variables,
\begin{equation}
\Phi = \frac{1}{r} \sum_{\omega \ell m} \phi_{\omega \ell}(r)  Y_{lm}(\theta, \phi) e^{-i \omega t} ,
\end{equation}
leads to a radial equation of the form
\begin{equation}
\label{H_Radial_equation}
\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0,
\end{equation}
where $r^\ast$ denotes the \emph{tortoise coordinate} defined by  $dr/dr^\ast =\sqrt{f(r)h(r)}$, and $V_{\ell}(r)$
is the effective potential.

@@

Effective potentials for the incompressible model are shown in Fig.~\ref{}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound). In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ behaviour of $h(r)$. The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V^{(ax)} &= - \frac{3Mf(R)}{R^3} , 
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V \equiv \lim_{\epsilon \rightarrow 0} \left\{ V(R + \epsilon) - V(R - \epsilon) \right\} . 
\end{equation}

>>>>

We shall consider a scalar wave $\Phi(x)$ on the compact body spacetime governed by the Klein-Gordon equation
\begin{equation}
\Box \Phi \equiv \frac{1}{\sqrt{-g}} \partial_{\mu} \left( \sqrt{-g} g^{\mu \nu} \partial_{\nu} \Phi \right) = 0
\end{equation}
where $g^{\mu \nu}$ is the inverse metric 
$
g = - f(r) h^{-1}(r) r^4 \sin^2 \theta
$
and is the metric determinant. Performing a standard separation of variables,
\begin{equation}
\Phi = \frac{1}{r} \sum_{\omega \ell m} \phi_{\omega \ell}(r)  Y_{lm}(\theta, \phi) e^{-i \omega t} ,
\end{equation}
leads to a radial equation of the form
\begin{equation}
\label{H_Radial_equation}
\left[\frac{d^{2}}{dr_{\ast}^{2}}+\omega^{2}-V_{\ell}(r)\right]\phi_{\omega\ell}= 0,
\end{equation}
where $V_{\ell}(r)$ is the effective potential, and $r^\ast$ denotes the \emph{tortoise coordinate} defined by  
\begin{equation}
dr/dr^\ast =\sqrt{f(r)h(r)} .  \label{eq:tortoise}
\end{equation}

@@

Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object with $R = 2.26M$ (i.e.~close to the Buchdahl bound). In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ behaviour of $h(r)$. The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V^{(ax)} &= - \frac{3Mf(R)}{R^3} , 
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V \equiv \lim_{\epsilon \rightarrow 0} \left\{ V(R + \epsilon) - V(R - \epsilon) \right\} . 
\end{equation}

 \begin{figure}[htb]
\centering
 \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v2} \\ \vspace{0.2cm}
 \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2}
\caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower). The scalar field and axial gravitational-wave potentials are indicated as solid/black lines and dotted/red lines, respectively. The horizontal axis is the tortoise coordinate $r_\ast$ defined in Eq.~(\ref{eq:tortoise}).}
\label{fig:Veff}
\end{figure}
